Compositional equivalences based on Open pNets

### 2020-03-12 2016-Weak-FH-Bisim/WeakBisim.tex
small push

\ERIC{Non... En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous... Voir page 21-22. On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}

@@

 \smallskip\noindent
 \[  OT_1  = \openrule{
      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [m=m'],  \{s1\_m\gets m\}
                      }
    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
    \]

    \smallskip
    The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
    $Post$ uses the variable $m$ from the action of hole $P$ to set the
    value of the sender state variable named $s1\_m$.

@@

%\subsection{Computing and using open automata}
%\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
%In this section we present a simple algorithm to construct the open
%automaton representing the behaviour of an open pNet, and we prove that
%under reasonable conditions this automaton is finite.
%
%\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
%This is a standard residual algorithm over a set of open-automaton
%states, but where transitions are open transitions
%constructively ``proven'' by deduction trees.
%
%1) Start with a set of unexplored states containing the initial state
%of the automaton, and an empty set of explored states.
%
%2) While there are unexplored states, pick one state from the
%unexplored set and add it to the explored set.
%
%2a- From this state
%build all possible deduction trees by application of the structural
%rules \TrUn\ and \TrDeux, using all applicable combinations
%of synchronisation vectors.
%In practice, the algorithm does not explicitely construct the
%deduction tree, but for each pNet node, builds all possible
%combinations of the OTs of its subnets, and filter these combinations
%by matching with all synchronisation vectors. 
% 
%2b- For each OT built, add the transition in the
%outgoing transitions of the current state, and add the
%resulting state in the unexplored set if it is not already there.
%
%3) The predicate is submitted to Z3 for checking satisfiability. If it
%is NOT satisfiable, the resulting OT is discarded. This will minimize
%the number of resulting transitions, and by reachability analysis,
%reduce the resulting open automaton.
%
%\end{algorithm}

@@

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}.

%    \begin{figure}[ht]
  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
%  \caption{Open Automaton of the Simple Protocol Implementation}  %\label{SimpleProtCounter:ImplOA}
%\end{figure}

@@

As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]

>>>>

\ERIC{Heu Non... 
  En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous... Voir page 21-22. On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}

@@

 \smallskip\noindent
 \[  OT_1  = \openrule{
      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
        \{\texttt{s1\_m}\gets \texttt{m}\}
                      }
    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
    \]

    \smallskip
    The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
    $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
    value of the sender state variable named $\texttt{s1\_m}$.

@@

@@

\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
For later references, we give to the transitions of this (strong)
Specification automaton as $SS_i$ while transitions of the
Implementation automaton will be labelled $SI_i$. In the figure we
have annotated each global state with the set of corresponding state variables.

@@

As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
Thus we define $\vis{\set\beta}$\footnote{\ERIC{La notation
    $\vis{\beta}$ n'est pas tres parlante, mais je n'ai pas vraiment
    de meilleure idee...}} as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
 \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
